Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-02 manuscript.Rmd
Updates to raw event plots

@@

# plot the time series
raw_events_ts_target <- ggplot() +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_target, colour = 'all events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=pos_events_target, colour = 'positive events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=neg_events_target, colour = 'negative events')) +
  scale_color_manual(values = c("red", "orange", "blue")) +
  xlab("Date") +
  ylab("Number of events") +
  ylim(0, 360)

@@

# plot the time series
raw_events_ts_source_target <- ggplot() +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_source_target, colour = 'all events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=pos_events_source_target, colour = 'positive events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=neg_events_source_target, colour = 'negative events')) +
  scale_color_manual(values = c("red", "orange", "blue")) +
  xlab("Date") +
  ylab("Number of events") +
  ylim(0, 360)

>>>>

# specify global plotting variables for easier testing
all_event_color = "#CC79A7"
positive_event_color = "#0072B2"
negative_event_color = "#D55E00"
line_thickness = 2

@@

# plot the time series
raw_events_ts_target <- ggplot() +
  geom_line(event_df, 
            mapping = aes(x= as.Date(Date), 
                          y=all_events_target, 
                          colour = 'all events')) +
  geom_line(event_df, 
            mapping = aes(x= as.Date(Date), 
                          y=pos_events_target, 
                          colour = 'positive events')) +
  geom_line(event_df, 
            mapping = aes(x= as.Date(Date),
                          y=neg_events_target, 
                          colour = 'negative events')) +
  scale_color_manual(values = c(all_event_color, # all
                                positive_event_color, # positive
                                negative_event_color)) + # negative
  scale_size_manual(values=line_thickness) +
  xlab("Date") +
  ylab("Number of events") +
  ylim(0, 360)

@@

# plot the time series
raw_events_ts_source_target <- ggplot() +
  geom_line(event_df, 
            mapping = aes(x = as.Date(Date), 
                          y=all_events_source_target, 
                          colour = 'all events')) +
  geom_line(event_df, 
            mapping = aes(x = as.Date(Date),
                          y=pos_events_source_target, 
                          colour = 'positive events')) +
  geom_line(event_df, 
            mapping = aes(x = as.Date(Date), 
                          y=neg_events_source_target, 
                          colour = 'negative events')) +
  scale_color_manual(values = c(all_event_color, # all
                                positive_event_color, # positive
                                negative_event_color)) + # negative
  scale_size_manual(values=line_thickness) +
  xlab("Date") +
  ylab("Number of events") +
  ylim(0, 360)
